\documentclass[11pt, oneside]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for rotated page geometry
%\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex		
\usepackage{amssymb}

\usepackage{fancyhdr}
\pagestyle{fancy}

\lhead{Mehta, Jash
		- mehtaj8\\
		Sharma, Aditya
		- shara24\\
		Ren, Zackary
		- renx11}
\rhead{\today}

\title{Project Approval}
\author{}
%\date{}							% Activate to display a given date or no date
%\begin{header}

%\end{header}
\begin{document}
%\maketitle
\marginpar{}
\section*{Project Approval Document}
\textbf{Team Name:} Euneva\\
\\
\textbf{Original Project Name:} Euneva\\
\textbf{Software Purpose:} Provide an automated task organization software to help students manage their course deadlines.\\
\textbf{Software Scope:} McMaster Students\\
\textbf{URL for original project:} https://github.com/irfansener/react-native-todo\\
\\
\textbf{Specialized hardware requirements?} N/A\\
\textbf{Any Software licenses required that McMaster does not own?} No\\
\textbf{Programming Languages:} Typescript, React Native, Python, Node.js\\
\\
\textbf{Is programming language feasible for your team?} Yes\\
\textbf{Is the domain knowledge understandable within one term?} Yes\\
\textbf{Number of lines of code:} 1140\\
\textbf{License:} Open Source\\
\textbf{License allows public redevelopment?} Yes\\
\textbf{Can you compile the original project's source code?} Yes\\
\textbf{What would be some test cases for the existing software?} N/A\\
\textbf{What changes do you intend to make to the project?} We will add web-scraping functionality, reminders functionality via (text, email and standard notification).\\

\end{document}  
